Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
add edits to section 6

The rule \infrule{I-out2} follows a similar line of reasoning. It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role. This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ disjoint incoming edges for the particular node at the top connecting it to the bottom.

The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles. This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$. The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with. The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.

The rule \infrule{I-striping} is the most complicated case.
It starts with the invariant L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints. The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each. The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology. In particular it uses the following inequality, where $g$ represents the size of the group for the role $n$:
%
\[ \begin{array}{c}
  (m-j)*e_1 \geq (n-g)*e_2
\end{array} \]
\noindent
%
The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each. Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.

@@

The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles. The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.

Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies. The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged. The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.

@@

The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths. When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$. 
%
When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$: 
%
$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
%
\noindent
The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.

>>>>

Consider rule \infrule{I-out2}, and consider any node in the role $n$. There are $e_2$ incoming edges to that node. Due to the fact that A$_m(j,k)$, we know that at least j of those $e_2$ edges are connected to nodes with disjoint paths from the origin. Hence we infer A$_n(1,min(j,e_2))$.

%The rule \infrule{I-out2} follows a similar line of reasoning. It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role. This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ disjoint incoming edges for the particular node at the top connecting it to the bottom.

The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles. This happens when the number of outgoing edges ($e_1$) nodes in role $m$ equals the number of nodes on top ($n$). \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with. \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.

The annotation $mincut(X)$ appearing on a n edge in an assertion about the fault tolerance between nodes in two roles. The rule \infrule{I-mincut} uses such assertions. To each node in role $n$, we can construct at least the minimum of $X$ and $k$ disjoint paths.

%The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles. The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.

The rule \infrule{I-striping} is the most complicated case.
It starts with the invariant L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints. The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each. The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology. In particular it uses the following inequality, where $g$ represents the size of the group for the role $n$:
%
\[ \begin{array}{c}
  (m-j)*e_1 \geq (n-g)*e_2
\end{array} \]
\noindent
%
The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least ``fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each. Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.

@@

Finally, rules \infrule{I-local} and \infrule{I-global} allow us to reason across pod hierarchies. The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged. The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.

@@

%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths. When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$. 
%
%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$: 
%
%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
%
%\noindent
%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
